Manuscript_Github_Pchabaudi_pir

### 2022-09-27 chapter4_results_chabaudi24h/Thesis_Github_Pchabaudi_pirAnalysis.Rmd
Change PCA plots to have capitalised RMT and colour blind colour scheme

@@

# (
#   plot <- ggplot(chab_tpm.df_pca_coords,
#                  aes(
#                    x = PC3,
#                    y = PC1,
#                    col = time,
#                    shape = transmission
#                  )) +
#     geom_point(size = 3,
#                alpha = 0.8) +
#     scale_color_manual(values = colornames) +
#     xlab(paste0('PC3 ', round(pca_importance$PC3[2]*100, digits = 1),'%')) +
#     ylab(paste0('PC1 ', round(pca_importance$PC1[2]*100, digits = 1),'%')) +
#     guides(shape=guide_legend(ncol=2),
#            col = guide_legend(ncol=2)) +
#     theme_classic() +
#     theme(legend.key.size = unit(4, 'mm'),
#           legend.text = element_text(size = 7))
# )

@@

chab_tpm_wPseudo.df_pca_coords <- data.frame(sample = rownames(chab_tpm_wPseudo.df_pca_var$coord),
                                        PC1 = chab_tpm_wPseudo.df_pca_coords$Dim.1,
                                        PC3 = chab_tpm_wPseudo.df_pca_coords$Dim.3,
                                        PC2 = chab_tpm_wPseudo.df_pca_coords$Dim.2) %>% 
  dplyr::mutate(stage = gsub(sample, pattern = '_[[:digit:]]$', replacement = '')) %>% 
  mutate( transmission = str_split_fixed(stage, pattern = '_', n = 2)[,1],
          time = str_extract(stage,pattern = '[[:digit:]]{1,2}h|sch.culture'))

colornames <- viridis(length(unique(chab_tpm_wPseudo.df_pca_coords$time)))
colornames <- setNames(colornames, 
                       sort(unique(chab_tpm_wPseudo.df_pca_coords$time)))

>>>>

chab_tpm.df_pca_coords <- data.frame(sample = rownames(chab_tpm.df_pca_var$coord),
                                        PC1 = chab_tpm.df_pca_coords$Dim.1,
                                        PC3 = chab_tpm.df_pca_coords$Dim.3,
                                        PC2 = chab_tpm.df_pca_coords$Dim.2) %>% 
  dplyr::mutate(stage = gsub(sample, pattern = '_[[:digit:]]$', replacement = '')) %>% 
  mutate( transmission = toupper(str_split_fixed(stage, pattern = '_', n = 2)[,1]),
          time = str_extract(stage,pattern = '[[:digit:]]{1,2}h|sch.culture'))

# colornames <- viridis(length(unique(chab_tpm.df_pca_coords$time)))
colornames <- c(cbPalette, 'black')
# colornames <- c('#FEFE62', '#D35FB7','#FFC20A', '#0C7BDC',
#                 '#1AFF1A', '#4B0092', '#E66100', '#5D3A9B',
#                 '#D41159')
colornames <- setNames(colornames, 
                       sort(unique(chab_tpm.df_pca_coords$time)))

@@

@@

chab_tpm_wPseudo.df_pca_coords <- data.frame(sample = rownames(chab_tpm_wPseudo.df_pca_var$coord),
                                        PC1 = chab_tpm_wPseudo.df_pca_coords$Dim.1,
                                        PC3 = chab_tpm_wPseudo.df_pca_coords$Dim.3,
                                        PC2 = chab_tpm_wPseudo.df_pca_coords$Dim.2) %>% 
  dplyr::mutate(stage = gsub(sample, pattern = '_[[:digit:]]$', replacement = '')) %>% 
  mutate( transmission = toupper(str_split_fixed(stage, pattern = '_', n = 2)[,1]),
          time = str_extract(stage,pattern = '[[:digit:]]{1,2}h|sch.culture'))

# colornames <- viridis(length(unique(chab_tpm_wPseudo.df_pca_coords$time)))
# colornames <- setNames(colornames, 
#                        sort(unique(chab_tpm_wPseudo.df_pca_coords$time)))
